---
title: "Midpoint Deliverable"
author: "Jenny Dao, Stephanie Nguyen, Janet Pan, & Dana Rin"
date: "5/18/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("temperature-chart.R")
source("CAT_data.R")
source("summary_info.R")
```

## Introduction

## Summary Information
In the Country Level Dataset, we are able to access data regarding the different types of waste and amounts of those wastes for every country. This data set accounts for a global population of `r world_pop`. Using this we calculated the total waste per person, which equaled `r avg_per_person`. On a larger scale, we calculated that there is an average of `r avg_total_waste` per country. When looking closer at the different types of waste created per country, we were able to calculate that there is an average of `r avg_agri_waste` of agricultural waste per country. Agriculture is such a large part of what goes into the make up of society around the globe. To better understand this data, with regards to location, we were able to determine the average total waste per person in the United States. This ended up being `r avg_per_person_us` per person.

## Summary Table

## Change in Temperature Map
```{r map, echo=FALSE}
map
```

This map helps answer which part of the world is being affected by global warming the most. The change in temperature was measured by the earliest date and latest date recorded with their corresponding average temperature. By subtracting the two, we can see the change in temperature over the years. The higher the change, the more affected by global warming a country is. This map is a good way to visualize it because we can clearly see, by the colors, which country is most affected and in what way. Based on this map, we can conclude that Russia is the country that is most affected by global warming. We can also see that Russia's temperature change is extremely positive, which means the country's surface temperature increased drastically over the years. There were also countries that actually had a negative temperature change, which means they actually got colder over the years, and based on the map, it seems that the countries closer to the south had a decrease in surface temperature.

## Climate Action Tracker (CAT) bar chart
```{r plot, echo=FALSE}
plot
```

This bar chart helps answer which has contributes the most to global warming, and will continue to do so in the future. The data in the chart represents the average value of contribution to climate global warming for each country. The total value accounts for oil and gas production,...

## Chart 3
